### 2017-08-18 Paper01_EnthalpyAndCrystallization.tex
Results - Enthalpy Tables - Added decon totals to last column, and degree C to Tx tables
Sub - Image - added Normalised dynamic xrd to the suplimentary section

\begin{table}[h]
	\centering
	\begin{tabular}{ c c c c c c c }
		\toprule
		Heating Rate \acrshort{ht} & \acrshort{Tg} & $T_{x1}$ & $T_{x2}$ & $T_{x3}$ & $T_{x4}$ & $T_{x5}$ \\ 
		$K/min$ & & & & & & \\
		\midrule
		100 & 136.1 & 164.8 & 193.4 & 201.8 & 240.2 & 262.4 \\
		80  & 132.0 & 160.0 & 194.4 & 201.9 & 238.2 & 260.3 \\
		60  & 129.6 & 157.7 & 190.0 & 197.8 & 232.9 & 259.0 \\
		40  & 126.6 & 155.2 & 189.0 & 200.0 & 226.4 & 254.7 \\
		30  & 126.2 & 151.5 & 187.0 & 198.4 & 221.0 & 251.1 \\
		20  & 125.1 & 149.8 & 188.4 & 197.0 & 216.0 & 246.8 \\
		15  & 123.8 & 148.3 & 186.2 & 195.6 & 212.2 & 243.9 \\
		10  & 123.5 & 144.5 & 183.4 & 192.9 & 207.4 & 239.8 \\
		5   & 120.5 & 141.1 & 179.7 & 187.5 & 199.8 & 232.7 \\ 
		\bottomrule
	\end{tabular}
	\caption{Bulk \MgZnCa~ alloy onset temperatures for the various \acrshort{dsc} \acrfullpl{ht}. All temperatures are in \degree C.}
	\label{tab:BulkOnsets}
\end{table}

\begin{table}[h]
	\centering
	\begin{tabular}{ c c c c c c c }
		\toprule
		Heating Rate \acrshort{ht} & \acrshort{Tg} & $T_{x1}$ & $T_{x2}$ & $T_{x3}$ & $T_{x4}$ & $T_{x5}$ \\ 
		$K/min$ & & & & & & \\
		\midrule
		100 & 108.5 & 128.6 &  & 177.3 &  & 240.3 \\
		80  & 106.0 & 121.2 &  & 165.6 &  & 238.8 \\
		60  & 107.3 & 134.0 &  & 176.1 &  & 237.8 \\
		40  & 100.2 & 119.8 &  & 170.7 &  & 234.2 \\
		30  & 95.3  & 110.4 &  & 169.5 &  & 232.5 \\
		20  & 95.5  & 115.2 &  & 170.5 &  & 229.4 \\
		15  & 92.5  & 113.5 &  & 168.8 &  & 224.0 \\
		\bottomrule
	\end{tabular}
	\caption{Film \MgZnCa~ alloy onset temperatures for the various \acrshort{dsc} \acrfullpl{ht}. All temperatures are in \degree C.}
	\label{tab:FilmOnsets}
\end{table}

@@

\begin{table}[h]
	\centering
	\begin{tabular}{ c c c c c c }
		\toprule
		Heating Rate \acrshort{ht} & $h_{T_{x1}}$ & $h_{T_{x2}}$ & $h_{T_{x3}}$ & $h_{T_{x4}}$ & $h_{T_{x5}}$ \\ 
		$K/min$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ \\
		\midrule
		100  & 59.59 & 6.97 & 49.16 & 22.84 & 46.08 \\
		80   & 42.61 & 6.08 & 32.33 & 18.27 & 31.25 \\
		60   & 30.02 & 4.05 & 25.41 & 16.76 & 19.81 \\
		40   & 16.93 & 4.36 & 12.44 & 11.13 & 11.68 \\
		30   & 12.03 & 3.68 & 9.32  & 9.18  & 9.02  \\
		20   & 7.18  & 2.21 & 4.99  & 5.67  & 5.78  \\
		15   & 5.48  & 2.01 & 3.65  & 4.69  & 4.43  \\
		10   & 3.45  & 1.43 & 2.28  & 3.14  & 2.92  \\
		5    & 1.65  & 0.69 & 1.09  & 1.47  & 1.42  \\
		\bottomrule
	\end{tabular}
	\caption{Bulk \MgZnCa~ alloy \acrfull{h} of crystallisation formation for $Tx_{1-5}$ for the various \acrshort{dsc} \acrfullpl{ht}; \gls{h} is in $J/g$.}
	\label{tab:Bulk_Enthalpy}
\end{table}

\begin{table}[h]
	\centering
	\begin{tabular}{ c c c c c c }
		\toprule
		Heating Rate \acrshort{ht} & $h_{T_{x1}}$ & $h_{T_{x2}}$ & $h_{T_{x3}}$ & $h_{T_{x4}}$ & $h_{T_{x5}}$ \\ 
		$K/min$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ \\
		\midrule
		100  & 48.24 &    & 49.85 &    & 43.38 \\
		80   & 43.27 &    & 53.56 &    & 36.18 \\
		60   & 15.5  &    & 8.78  &    & 22.4  \\
		40   & 16.22 &    & 9.13  &    & 16.27 \\
		30   & 13.72 &    & 7.16  &    & 11.81 \\
		20   & 6.16  &    & 2.3   &    & 7.45  \\
		15   & 6.99  &    & 3.66  &    & 6.57  \\
		\bottomrule
	\end{tabular}
	\caption{Film \MgZnCa~ alloy \acrfull{h} of crystallisation formation for $Tx_{1-5}$ for the various \acrshort{dsc} \acrfullpl{ht}; \gls{h} is in $J/g$.}
	\label{tab:Film_Enthalpy}
\end{table}

@@

>>>>

\begin{table}[h]
	\centering
	\begin{tabular}{ c c c c c c c }
		\toprule
		Heating Rate \acrshort{ht} & \acrshort{Tg} & $T_{x1}$ & $T_{x2}$ & $T_{x3}$ & $T_{x4}$ & $T_{x5}$ \\ 
		$K/min$ & \degree C & \degree C & \degree C & \degree C & \degree C & \degree C \\
		\midrule
		100 & 136.1 & 164.8 & 193.4 & 201.8 & 240.2 & 262.4 \\
		80  & 132.0 & 160.0 & 194.4 & 201.9 & 238.2 & 260.3 \\
		60  & 129.6 & 157.7 & 190.0 & 197.8 & 232.9 & 259.0 \\
		40  & 126.6 & 155.2 & 189.0 & 200.0 & 226.4 & 254.7 \\
		30  & 126.2 & 151.5 & 187.0 & 198.4 & 221.0 & 251.1 \\
		20  & 125.1 & 149.8 & 188.4 & 197.0 & 216.0 & 246.8 \\
		15  & 123.8 & 148.3 & 186.2 & 195.6 & 212.2 & 243.9 \\
		10  & 123.5 & 144.5 & 183.4 & 192.9 & 207.4 & 239.8 \\
		5   & 120.5 & 141.1 & 179.7 & 187.5 & 199.8 & 232.7 \\ 
		\bottomrule
	\end{tabular}
	\caption{Bulk \MgZnCa~ alloy onset temperatures for the various \acrshort{dsc} \acrfullpl{ht}. All temperatures are in \degree C.}
	\label{tab:BulkOnsets}
\end{table}

\begin{table}[h]
	\centering
	\begin{tabular}{ c c c c c c c }
		\toprule
		Heating Rate \acrshort{ht} & \acrshort{Tg} & $T_{x1}$ & $T_{x2}$ & $T_{x3}$ & $T_{x4}$ & $T_{x5}$ \\ 
		$K/min$  & \degree C & \degree C & \degree C & \degree C & \degree C & \degree C \\
		\midrule
		100 & 108.5 & 128.6 &  & 177.3 &  & 240.3 \\
		80  & 106.0 & 121.2 &  & 165.6 &  & 238.8 \\
		60  & 107.3 & 134.0 &  & 176.1 &  & 237.8 \\
		40  & 100.2 & 119.8 &  & 170.7 &  & 234.2 \\
		30  & 95.3  & 110.4 &  & 169.5 &  & 232.5 \\
		20  & 95.5  & 115.2 &  & 170.5 &  & 229.4 \\
		15  & 92.5  & 113.5 &  & 168.8 &  & 224.0 \\
		\bottomrule
	\end{tabular}
	\caption{Film \MgZnCa~ alloy onset temperatures for the various \acrshort{dsc} \acrfullpl{ht}. All temperatures are in \degree C.}
	\label{tab:FilmOnsets}
\end{table}

@@

\begin{table}[h]
	\centering
	\begin{tabular}{ c c c c c c c }
		\toprule
		Heating Rate \acrshort{ht} & $h_{T_{x1}}$ & $h_{T_{x2}}$ & $h_{T_{x3}}$ & $h_{T_{x4}}$ & $h_{T_{x5}}$ & $h_{Total}$ \\ 
		$K/min$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ \\
		\midrule
		100 & 59.59 & 6.97 & 49.16 & 22.84 & 46.08 & 184.64 \\
		80  & 42.61 & 6.08 & 32.33 & 18.27 & 31.25 & 130.54 \\
		60  & 30.02 & 4.05 & 25.41 & 16.76 & 19.81 & 96.05  \\
		40  & 16.93 & 4.36 & 12.44 & 11.13 & 11.68 & 56.54  \\
		30  & 12.03 & 3.68 & 9.32  & 9.18  & 9.02  & 43.23  \\
		20  & 7.18  & 2.21 & 4.99  & 5.67  & 5.78  & 25.83  \\
		15  & 5.48  & 2.01 & 3.65  & 4.69  & 4.43  & 20.26  \\
		10  & 3.45  & 1.43 & 2.28  & 3.14  & 2.92  & 13.22  \\
		5   & 1.65  & 0.69 & 1.09  & 1.47  & 1.42  & 6.32   \\
		\bottomrule
	\end{tabular}
	\caption{Bulk \MgZnCa~ alloy \acrfull{h} of crystallisation formation for $Tx_{1-5}$ for the various \acrshort{dsc} \acrfullpl{ht}; \gls{h} is in $J/g$.}
	\label{tab:Bulk_Enthalpy}
\end{table}

\begin{table}[h]
	\centering
	\begin{tabular}{ c c c c c c c }
		\toprule
		Heating Rate \acrshort{ht} & $h_{T_{x1}}$ & $h_{T_{x2}}$ & $h_{T_{x3}}$ & $h_{T_{x4}}$ & $h_{T_{x5}}$ & $h_{Total}$ \\ 
		$K/min$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ \\
		\midrule
		100 & 48.24 &  & 49.85 &  & 43.38 & 141.47 \\
		80  & 43.27 &  & 53.56 &  & 36.18 & 133.01 \\
		60  & 15.5  &  & 8.78  &  & 22.4  & 46.68  \\
		40  & 16.22 &  & 9.13  &  & 16.27 & 41.62  \\
		30  & 13.72 &  & 7.16  &  & 11.81 & 32.69  \\
		20  & 6.16  &  & 2.3   &  & 7.45  & 15.91  \\
		15  & 6.99  &  & 3.66  &  & 6.57  & 17.22  \\
		\bottomrule
	\end{tabular}
	\caption{Film \MgZnCa~ alloy \acrfull{h} of crystallisation formation for $Tx_{1-5}$ for the various \acrshort{dsc} \acrfullpl{ht}; \gls{h} is in $J/g$.}
	\label{tab:Film_Enthalpy}
\end{table}

@@

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.85\textwidth]{XRD_Normalised_Dynamic_BulkFilm_Facet.png}
	\caption{Supplementary: Normalised dynamic \acrshort{xrd} pattern for both bulk and film \MgZnCa~ heated incrementally \textit{in-situ} from $35-185$\degree C for crystallisation peak identified from \acrshort{dsc}. Bulk is shown in black, and film in red. Note the Al substrate and other high intensity peaks have been faceted as to not dwarf all other peaks.}
	\label{fig:XRD_Dynamic_BulkandFilm}
\end{figure}
